Verification of concurrent design patterns with data

### 2019-02-19 2018-Arch-pNets/arch-pNets.tex
arch-pNets paper: Minor edits :

\addSB{%
%
For the sake of clarity, we simplify the encoding in
\fig{FailureTimer:pNet} by reusing the port names of the original
architecture instead of fresh names $\alpha$.  This is made
possible by the fact that each synchronisation vector involves at
most one action of interest (see the properties in
\app{properties}).
%% In the general encoding, the global actions of the
%% synchronisation vectors should be fresh action names.
%% However,
%% for the properties considered in our case study, we only need to
%% exhibit the actions of the holes.  Furthermore, each
%% synchronisation vector involves at most one such action.
%% This
%% allows us to reuse them as the global actions of the
%% synchronisation vectors, simplifying the translation of
%% properties to be verified (\cf \app{properties}).
%
}\noteLH{ce
  paragraphe sonne vraiment note de rapport de recherche, tu
  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ? OUI -- Ludo}

@@

% \subsection{SMT encoding of open pNets}
% \label{secn:smt}

@@

\paragraph{Practical experiments.}\noteSB{J'ai repris ce paragraphe}
\noteLH{j ai nomme ce paragraphe}
The above encoding provides a mechanism for the symbolic verification
of architectures using our existing tool
\cite{HMZ-FORTE2016QBMZ-AVOCS18} to compute the open automaton
semantics of an open pNet. This tool computes open transitions from
pLTS behaviours and synchronisation vectors of the pNet, then uses an
SMT engine to check satisfiability of their predicates, minimizing the
size of the resulting automaton.
%% The encoding into the SMT language involves the definition of the
%% action and data domains and operators, and the axiomatisation of
%% domain-dependant properties, to allow the SMT engine to be as precise
%% as possible (even if it cannot be complete).
%% The resulting open automaton will later be subject to (symbolic)
%% model-checking and equivalence checking algorithms, themselves
%% requiring automatic proof assistance. \todoEM{trop flou pour le
%%   moment, mais je n'ose pas dire des trucs trop precis... meme si on a
%%   deja une implem de la FH-bisim, elle n'est pas validee!}

@@

@@

  In particular, the first safety property \eq{prop:reset:can}:
  \begin{equation*}
    \AG \bigl(\PortFail(true) \rightarrow \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
  \end{equation*}
is not true, because the $OT_2$ loop on state $\ostate{11}$ stays in
state 11 where you need another $\PortFail(true)$ before enabling a
reset. This is because without priorities we can have an
activity on the dandling ``fail'' port without synchronising with the
others, even if they are available.

>>>>

\addSB{%
%
For the sake of clarity, we simplify the case study encoding in
\fig{FailureTimer:pNet} by reusing the port names of the original
architecture instead of fresh names $\alpha$.  This is made
possible by the fact that each synchronisation vector involves at
most one action of interest (see the properties in
\app{properties}).
%% In the general encoding, the global actions of the
%% synchronisation vectors should be fresh action names.
%% However,
%% for the properties considered in our case study, we only need to
%% exhibit the actions of the holes.  Furthermore, each
%% synchronisation vector involves at most one such action.
%% This
%% allows us to reuse them as the global actions of the
%% synchronisation vectors, simplifying the translation of
%% properties to be verified (\cf \app{properties}).
%
}\noteLH{ce
  paragraphe sonne vraiment note de rapport de recherche, tu
  arrives a lui donner un peu d'abstraction/de recul?}\noteSB{Est-ce que c'est mieux comme \c{c}a ? OUI -- Ludo}

@@

%% \subsection{SMT encoding of open pNets}
% \label{secn:smt}

@@

\paragraph{Practical experiments}\noteSB{J'ai repris ce paragraphe}
\noteLH{j ai nomme ce paragraphe}
The above encoding provides a mechanism for the symbolic verification
of architectures using our existing tool
\cite{HMZ-FORTE2016QBMZ-AVOCS18} to compute the open automaton
semantics of an open pNet. This tool computes open transitions from
pLTS behaviours and synchronisation vectors of the pNet, then uses an
SMT engine to check satisfiability of their predicates, minimizing the
size of the resulting automaton.
%% The encoding into the SMT language involves the definition of the
%% action and data domains and operators, and the axiomatisation of
%% domain-dependant properties, to allow the SMT engine to be as precise
%% as possible (even if it cannot be complete).
%% The resulting open automaton will later be subject to (symbolic)
%% model-checking and equivalence checking algorithms, themselves
%% requiring automatic proof assistance. \todoEM{trop flou pour le
%%   moment, mais je n'ose pas dire des trucs trop precis... meme si on a
%%   deja une implem de la FH-bisim, elle n'est pas validee!}

@@

\noindent
\add{The following appendices are included for convenience and would be integrated into a research report if the paper is accepted for publication. The first appendix provides previously published complementary information, whereas the subsequent ones give additional formal details complementing architecture definitions, proofs of theorems, and the case study.}

@@

  In particular, the first safety property \eq{prop:reset:can}:
  \begin{equation*}
    \AG \bigl(\PortFail(true) \rightarrow \EX \EU[]{\lnot \PortFail(true)}{\PortReset}\bigr).
  \end{equation*}
is not true, because the $OT_2$ loop on state $\ostate{11}$ stays in
state 11 where you need another $\PortFail(true)$ before enabling a
reset. This is because without priorities we can have an
activity on the dandling ``fail'' port without synchronising with the
others, even if they are available.
